Bibat: Batteries-include Bayesian Analysis Template

### 2024-01-25 paper/main.qmd
Small paper update

Bibat accommodates this ubiquitous scenario by introducing an abstraction called
"fitting mode" and a corresponding Pydantic base class `FittingMode`, along with
and several subclasses for commonly used cases.

This abstraction allows bibat projects to handle fitting a model and dataset in
different ways appropriately and flexibly. For example, the provided prior
sampling fitting mode creates a Stan input dictionary with the `likelihood`
data variable set to `0`, performs MCMC sampling and writes data to the
`InferenceData` group `prior`.

@@

There is some software that addresses the general task of facilitating Bayesian
workflow, but differently from bibat. For example, bambi [@capretto2020]
and brms [@burknerBrmsPackageBayesian2017] aim to make implementing Bayesian
workflows easier by trivialising the task of specifying a Bayesian generalised
linear model and fitting it to a single tabular dataset. This approach does not
address several difficulties that bibat does address,

>>>>

Bibat accommodates this ubiquitous scenario by introducing an abstraction called
"fitting mode". This abstraction allows bibat projects to handle fitting a
model and dataset in different ways appropriately and flexibly. For example, the
provided prior sampling fitting mode creates a Stan input dictionary with the
`likelihood` data variable set to `0`, performs MCMC sampling and writes data
to the `InferenceData` group `prior`. Bibat provides fitting modes corresponding
for prior sampling, posterior sampling and kfold posterior sampling. Users can
easily add additional fitting modes by copying these examples.

@@

There is some software that addresses the general task of facilitating Bayesian
workflow, but differently from bibat. For example, bambi [@capretto2020]
and brms [@burknerBrmsPackageBayesian2017] aim to make implementing Bayesian
workflows easier by providing ergonomic ways to specify and fit Bayesian
generalised models to tabular datasets. Bibat is complementary with these
packages, as it targets use cases that they do not support, such as analyses
where complex datasets or models might be required.

#
